Blog post: Smart quotes, em dashes, and en dashes

### 2020-07-22 text/20/codes-for-covid-19.Rmd
Change to categories, part 8

---
title: "Codes for COVID-19 in the electronic health record"
author: "Steve Simon"
source: "New"
date: "2020-04-15"
category: Blog post
tags: Electronic health records
output: html_document
---

>>>>

---
title: "Codes for COVID-19 in the electronic health record"
author: "Steve Simon"
source: "New"
date: "2020-04-15"
categories: Blog post
tags: Electronic health records
output: html_document
---

### 2020-07-22 text/20/ihme-covid-model.Rmd
Change to categories, part 8

---
title: "Criticisms of the IHME COVID-19 model"
author: "Steve Simon"
source: "New"
category: Blog post
tags: Epidemiology
output: html_document
---

>>>>

---
title: "Criticisms of the IHME COVID-19 model"
author: "Steve Simon"
source: "New"
categories: Blog post
tags: Epidemiology
output: html_document
---

### 2020-07-22 text/20/map-projections.Rmd
Change to categories, part 8

---
title: "Blog post: Different map projections"
author: "Steve Simon"
source: "New"
date: "2020-03-15"
category: Blog post
tags: Graphical display
output: html_document
---

>>>>

---
title: "Blog post: Different map projections"
author: "Steve Simon"
source: "New"
date: "2020-03-15"
categories: Blog post
tags: Graphical display
output: html_document
---

### 2020-07-22 text/20/misuse-of-gradient.Rmd
Change to categories, part 8

---
title: "Blog post: An example of a poor color choice"
author: "Steve Simon"
source: "New"
date: "2020-03-11"
category: Blog post
tags: Graphical display
output: html_document
---

>>>>

---
title: "Blog post: An example of a poor color choice"
author: "Steve Simon"
source: "New"
date: "2020-03-11"
categories: Blog post
tags: Graphical display
output: html_document
---

### 2020-07-22 text/20/non-breaking-space.Rmd
Change to categories, part 8

---
title: "Blog post: Identifying and manipulating non-breaking spaces"
author: "Steve Simon"
source: "New"
date: "2020-01-07"
category: Blog post
tags: Data management
output: html_document
---

>>>>

---
title: "Blog post: Identifying and manipulating non-breaking spaces"
author: "Steve Simon"
source: "New"
date: "2020-01-07"
categories: Blog post
tags: Data management
output: html_document
---

### 2020-07-22 text/20/reading-text-files.Rmd
Change to categories, part 8

---
title: "Reading text files"
author: "Steve Simon"
source: "New"
date: "Created: 2020-04-30"
category: Blog post
tags: Data management
output: html_document
---

>>>>

---
title: "Reading text files"
author: "Steve Simon"
source: "New"
date:2020-04-30"
categories: Blog post
tags: Data management
output: html_document
---

### 2020-07-22 text/20/smart-quotes.Rmd
Change to categories, part 8

---
title: "Blog post: Smart quotes, em dashes, and en dashes"
author: "Steve Simon"
source: "New"
date: "2020-03-02"
category: Blog post
tags: Data management
output: html_document
---

>>>>

---
title: "Blog post: Smart quotes, em dashes, and en dashes"
author: "Steve Simon"
source: "New"
date: "2020-03-02"
categories: Blog post
tags: Data management
output: html_document
---
